Network Structure, Efficiency, and Performance in WikiProjects

### 2017-08-07 paper.tex
Acknowledgements.

% Manuscript
\documentclass[10pt,twocolumn]{article}
\usepackage{natbib}

@@

% Document-specific packages
\usepackage{epigraph}

@@

To model the relationship between performance, efficiency, and network structure,
we must have a way to quantify performance and efficiency.
We define these quantities on a per-WikiProject basis to enable comparisons across different
projects.
Our definitions are inpsired by work modeling collective problem-solving as an optimization
problem \cite{}.
The effieincy quantifies how quikly a solution is reached,
while the performance quantifies how good the eventual solution is.

@@

\begin{table*}
\small
\begin{tabular}{lllllllll}
                               & Perf$^\dagger$ & Perf$^\dagger$ & A-Eff$^\dagger$ & A-Eff$^\dagger$ & B-Eff$^\dagger$ & B-Eff$^\dagger$ & C-Eff$^\dagger$ & C-Eff$^\dagger$ \\
\hline
Mean degree$^\dagger$          &  -0.8$^{***}$  &  -0.8$^{***}$
                               &  -0.6$^{**}$   &  -0.8$^{***}$
                               &  &
                               &  & \\
In-degree skewness$^\dagger$   &  -0.6$^{***}$  & \+ ---      
                               &  -0.4$^{**}$   & \+ ---      
                               &  & \+ ---      
                               &  & \+ ---      \\
Out-degree skewness$^\dagger$  &  \+ ---        & -0.5$^{***}$  
                               &  \+ ---        & -0.6$^{***}$
                               &  \+ ---        &
                               &  \+ ---        & \\
Mean path$^\dagger$            &  -0.36$^{***}$ & -0.36$^{***}$ 
                               &  -0.03         & -0.10
                               &  &
                               &  & \\
C-eff$^\dagger$                &  -0.08$^{**}$  & -0.08$^{**}$  
                               &  \+ ---        & \+ ---      
                               &  \+ ---        & \+ ---      
                               &  \+ ---        & \+ --- \\
Connectivity                   & \+0.02         & \+0.02        
                               &  \+0.08        & \+0.09
                               &  &
                               &  & \\
Mean editors/article$^\dagger$ & \+0.4$^{***}$  & \+0.4$^{***}$ 
                               & \+0.2          & \+0.3
                               &  &
                               &  & \\
Article count$^\dagger$        &  -0.3          & -0.3          
                               & \+0.6${^*}$    & \+0.7${^*}$ 
                               &  &
                               &  & \\
Editor count$^\dagger$         & \+0.7$^{*}$    & \+0.5         
                               & \+0.7$^{*}$    & \+1.0$^{**}$
                               &  &
                               &  & \\
Revision count$^\dagger$       & \+0.4          & \+0.4         
                               &  -0.8$^{**}$   & -0.9$^{**}$
                               &  &
                               &  & \\
First assessment               & \+0.03         & \+0.06        
                               & \+0.09$^{*}$   & \+0.10$^{**}$
                               &  &
                               &  & \\
Mean article age               &  -0.04         & -0.03         
                               &  -0.04         & -0.04
                               &  &
                               &  & \\
\hline
DoF                            & 1278           & 1278          
                               & 1048           & 1048
                               &  &
                               &  & \\
R$^2_{adj}$                    & 0.37           & 0.37          
                               & 0.15           & 0.16
                               &  &
                               &  & \\
\end{tabular}
\caption{
\label{tab:model}
}
\end{table*}

@@

\section{Acknowledgements}
Daniel Romero.
Danielle Livneh, Karthik Ramanathan.
Yan Chen, Tanya Rosenblat.
MIT Center for Civic Media.
Cooperation Working Group at the Harvard Berkman-Klein Center.
School of Information.

>>>>

% Manuscript
\documentclass[10pt,twocolumn]{article}
\usepackage[numbers]{natbib}

@@

% Document-specific packages
\usepackage{epigraph}
\usepackage[flushleft]{threeparttable}

@@

To model the relationship between performance, efficiency, and network structure,
we must have a way to quantify performance and efficiency.
We define these quantities on a per-WikiProject basis to enable comparisons across different
projects.
Our definitions are inpsired by work modeling collective problem-solving as an optimization
problem \cite{}.
The efficiency quantifies how quikly a solution is reached,
while the performance quantifies how good the eventual solution is.

@@

\begin{table*}
\small
\begin{tabular}{lllllllll}
                               & Perf$^\dagger$ & Perf$^\dagger$ & A-Eff$^\dagger$ & A-Eff$^\dagger$ & B-Eff$^\dagger$ & B-Eff$^\dagger$ & C-Eff$^\dagger$ & C-Eff$^\dagger$ \\
\hline
Mean degree$^\dagger$          &  -0.84$^{***}$  &  -0.78$^{***}$
                               &  -0.61$^{**}$   &  -0.84$^{***}$
                               &  -0.50$^{***}$  &  -0.61$^{***}$
                               &  -0.34$^{**}$   &  -0.31$^{*}$ \\
In-degree skewness$^\dagger$   &  -0.58$^{***}$  & \+ ---      
                               &  -0.43$^{**}$   & \+ ---      
                               &  -0.19          & \+ ---      
                               &  -0.1           & \+ ---      \\
Out-degree skewness$^\dagger$  &  \+ ---         &  -0.48$^{***}$  
                               &  \+ ---         &  -0.57$^{***}$
                               &  \+ ---         &  -0.26$^{*}$
                               &  \+ ---         &  -0.066 \\
Mean path$^\dagger$            &  -0.357$^{***}$ &  -0.356$^{***}$ 
                               &  -0.026         &  -0.096
                               &  -0.020         &  -0.045
                               &  -0.092$^{**}$  &  -0.086 \\
C-eff$^\dagger$                &  -0.083$^{**}$  & -0.085$^{**}$  
                               &  \+ ---         & \+ ---      
                               &  \+ ---         & \+ ---      
                               &  \+ ---         & \+ --- \\
Connectivity                   & \+0.018         & \+0.016        
                               & \+0.081         & \+0.088
                               & \+0.126$^{***}$ & \+0.142$^{***}$
                               & \+0.080$^{**}$  & \+0.081$^{**}$ \\
Mean editors/article$^\dagger$ & \+0.37$^{***}$  & \+0.40$^{***}$ 
                               & \+0.22          & \+0.27
                               & \+0.20          & \+0.22$^{*}$
                               & \+0.076         & \+0.075 \\
Article count$^\dagger$        &  -0.32          & -0.27          
                               & \+0.63${^*}$    & \+0.70${^*}$ 
                               & \+0.76$^{**}$   & \+0.78$^{**}$
                               & \+0.67$^{***}$  & \+0.67$^{***}$ \\
Editor count$^\dagger$         & \+0.68$^{*}$    & \+0.48         
                               & \+0.74$^{*}$    & \+0.97$^{**}$
                               & \+0.60$^{*}$    & \+0.72$^{**}$
                               & \+0.52$^{*}$    & \+0.46$^{*}$ \\
Revision count$^\dagger$       & \+0.37          & \+0.39         
                               &  -0.84$^{**}$   & -0.88$^{**}$
                               &  -1.05$^{***}$  & -1.05$^{***}$
                               &  -1.00$^{***}$  & -1.00$^{***}$ \\
First assessment               & \+0.028         & \+0.058        
                               & \+0.086$^{*}$   & \+0.101$^{**}$
                               & \+0.309$^{***}$ & \+0.321$^{***}$
                               & \+0.456$^{***}$ & \+0.460$^{***}$ \\
Mean article age               &  -0.040         & -0.029         
                               &  -0.049         & -0.037
                               &  -0.019         & -0.014
                               &  -0.046$^{*}$   & -0.045$^{*}$ \\
\hline
DoF                            & 1278            & 1278          
                               & 1048            & 1048
                               & 1371            & 1371
                               & 1540            & 1540 \\
R$^2_{adj}$                    & 0.37            & 0.37          
                               & 0.15            & 0.16
                               & 0.30            & 0.30
                               & 0.43            & 0.43 \\
\end{tabular}
\caption{Standardized coefficients for OLS models.
\label{tab:model}
}
\begin{tablenotes}
\item $\dagger$ Log-transformed. * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
\end{tablenotes}
\end{table*}

@@

\section{Acknowledgements}
I would like to thank Daniel Romero for valuable guidance and feedback;
Danielle Livneh and Karthik Ramanathan for help collecting the data sets;
Yan Chen and Tanya Rosenblat for feedback on the methodology;
and the atendees of the May 25, 2017 MIT Center for Civic Media lab meeting and
the Berkman-Klein Center's Cooperation Working Group for helpful feedback on
preliminary results.
This research was funded by the University of Michigan School of Information.
